The helicoverpa package

### 2021-08-26 notebook/helicoverpa_notes.Rmd
Add a notebook entry with output for the null simulations

    - **AUG** [19](#u-19-AUG-2021) 
    - **JUL** [23](#u-23-JUL-2021)

@@

@@

```{r}
library(jsonlite);
sim  <- toy_simulate_resistance(pathogens = 3, crops = 3);
json <- results_to_json(pest = sim$PEST_DATA[[19]], land = sim$LAND_DATA[[19]],
                        filename = "../data/sample_sim.json");
```

@@

```{r}
library(jsonlite);
sim_json <- results_to_json(sim = sim[[19]], 
                            filename = "../data/sample_sim.json");
```

>>>>

    - **AUG** [19](#u-19-AUG-2021), [26](#u-26-AUG-2021)
    - **JUL** [23](#u-23-JUL-2021)

@@

> <a name="u-26-AUG-2021">Update: 26 AUG 2021</a>

I have now run the same analysis that I did on [19 AUG 2021](#u-19-AUG-2021), but with traits that evolve independently. This was done by setting a covariance matrix to be the identity matrix for four traits. Here is the `mine_gmatrix` output that was used for the simulations.

```{r, echo = FALSE}
mg_2021_AUG_26 <- readRDS("data/2021_AUG_26_data/mg_n1.rds");
print(mg_2021_AUG_26);
```

Note that the parameter values for mining the matrix were identical to those chosen in the simulations from [19 AUG 2021](#u-19-AUG-2021). The results are as expected; all traits evolve in response to selection to feed on both crop types and resist both pesticide types.

![](images/2021_AUG_26/asexual_no_rotation_space_NULL.png)

![](images/2021_AUG_26/asexual_no_rotation_time_NULL.png)

![](images/2021_AUG_26/asexual_no_rotation_traits_NULL.png)

![](images/2021_AUG_26/asexual_pesticide_rotation_space_NULL.png)

![](images/2021_AUG_26/asexual_pesticide_rotation_time_NULL.png)

![](images/2021_AUG_26/asexual_pesticide_rotation_traits_NULL.png)

![](images/2021_AUG_26/asexual_both_rotation_space_NULL.png)

![](images/2021_AUG_26/asexual_both_rotation_time_NULL.png)

![](images/2021_AUG_26/asexual_both_rotation_traits_NULL.png)

![](images/2021_AUG_26/sexual_selfing_no_rotation_space_NULL.png)

![](images/2021_AUG_26/sexual_selfing_no_rotation_time_NULL.png)

![](images/2021_AUG_26/sexual_selfing_no_rotation_traits_NULL.png)

![](images/2021_AUG_26/sexual_selfing_pesticide_rotation_space_NULL.png)

![](images/2021_AUG_26/sexual_selfing_pesticide_rotation_time_NULL.png)

![](images/2021_AUG_26/sexual_selfing_pesticide_rotation_traits_NULL.png)

![](images/2021_AUG_26/sexual_selfing_both_rotation_space_NULL.png)

![](images/2021_AUG_26/sexual_selfing_both_rotation_time_NULL.png)

![](images/2021_AUG_26/sexual_selfing_both_rotation_traits_NULL.png)

![](images/2021_AUG_26/sexual_noselfing_no_rotation_space_NULL.png)

![](images/2021_AUG_26/sexual_noselfing_no_rotation_time_NULL.png)

![](images/2021_AUG_26/sexual_noselfing_no_rotation_traits_NULL.png)

![](images/2021_AUG_26/sexual_noselfing_pesticide_rotation_space_NULL.png)

![](images/2021_AUG_26/sexual_noselfing_pesticide_rotation_time_NULL.png)

![](images/2021_AUG_26/sexual_noselfing_pesticide_rotation_traits_NULL.png)

![](images/2021_AUG_26/sexual_noselfing_both_rotation_space_NULL.png)

![](images/2021_AUG_26/sexual_noselfing_both_rotation_time_NULL.png)

![](images/2021_AUG_26/sexual_noselfing_both_rotation_traits_NULL.png)

![](images/2021_AUG_26/biparental_no_rotation_space_NULL.png)

![](images/2021_AUG_26/biparental_no_rotation_time_NULL.png)

![](images/2021_AUG_26/biparental_no_rotation_traits_NULL.png)

![](images/2021_AUG_26/biparental_pesticide_rotation_space_NULL.png)

![](images/2021_AUG_26/biparental_pesticide_rotation_time_NULL.png)

![](images/2021_AUG_26/biparental_pesticide_rotation_traits_NULL.png)

![](images/2021_AUG_26/biparental_both_rotation_space_NULL.png)

![](images/2021_AUG_26/biparental_both_rotation_time_NULL.png)

![](images/2021_AUG_26/biparental_both_rotation_traits_NULL.png)

For full simulations, I think it will be important to have each replicate (and I'm including all of the above as one replicate) with its own mined gmatrix.

@@

```{r}
library(jsonlite);
sim  <- toy_simulate_resistance(pathogens = 3, crops = 3);
json <- results_to_json(pest = sim$PEST_DATA[[19]], land = sim$LAND_DATA[[19]],
                        filename = "toy_model/data/sample_sim.json");
```

@@

```{r}
library(jsonlite);
sim_json <- results_to_json(sim = sim[[19]], 
                            filename = "toy_model/data/sample_sim.json");
```
